
---
title: "B Cell (CD19+) and Macrophage (CD68+) Spatial Interaction in the Tumor Microenvironment Associated with Higher Survival Probability"
date: '`r format(Sys.time(), "%Y-%m-%d")`'
output:
  html_document: 
    code_folding: hide
    toc: true
    toc_float: true
hitheme: tomorrow
highlighter: highlight.js
knit: (function(inputFile, encoding) {
  rmarkdown::render(inputFile, encoding = encoding, output_dir = "../results") })
---


```{r setup, message=FALSE, echo=TRUE, warning=FALSE}

# html_document: 
 #   code_folding: hide
  #  toc: true
   # toc_float: true


library(tidyverse)
library(readxl)
library(janitor)
library(naniar)
library(phenoptr)
library(phenoptrReports)
library(rtree)
library(ggpubr)
library(zoo)
library(survival)
library(lubridate)
library(survminer)
library(reReg)
library(kableExtra)
library(table1)

knitr::opts_chunk$set(echo = FALSE,
  warning = FALSE,
  message = FALSE
)

suppressMessages(library(tidyverse))

theme_set(theme_bw() + theme(legend.position = "bottom"))

```


```{r}

#Reading in data 
ovarian_data <- read_cell_seg_data("~/Desktop/Research/MCR_Paper/data/Consolidated_data_copy.txt.zip")

# Keeping just tumor and stroma samples
ovarian_data = ovarian_data %>%
  filter(`Tissue Category` != "Glass")


#removing initial descriptor characters from `Sample Name` variable so as to match with the format of the clinical data 
ovarian_data$`Sample Name` = substr(ovarian_data$`Sample Name`, 21, 100)


# Creating a control variable to identify the four control samples that are not related to the ovarian study
ovarian_data = ovarian_data %>% mutate(control = case_when(
  `Sample Name` == "A_Core[1,7,A]_[6035,51922].im3" ~ 1,
  `Sample Name` == "A_Core[1,8,A]_[6099,54080].im3" ~ 1,
  `Sample Name` == "B_Core[1,7,A]_[5838,48555].im3" ~ 1,
  `Sample Name` == "B_Core[1,8,A]_[5838,50714].im3" ~ 1,
  TRUE ~ 0,
))

#Filtering out the four control studies

ovarian_data = ovarian_data %>% filter(control=="0")


## Creating phenotype variables for the combinations. This is done because in order to identify some cell types, one phenotype marker is not enough

ovarian_data = ovarian_data %>% mutate(`Phenotype CD3 CD8`=case_when(
  `Phenotype CD3` =="CD3+" & `Phenotype CD8`=="CD8+" ~ "CD3+ CD8+",
  `Phenotype CD3` =="CD3+" & `Phenotype CD8` =="CD8-" ~ "CD3+ CD8-",
  TRUE~ ""
))

#Joining clinical with data with ovarian data 


clinical_data <- read_excel("~/Desktop/Research/MCR_Paper/data/Clinical_Attributes_and_more.xlsx", 
col_types = c("numeric", "text", "numeric",  "text", "text", "numeric", "numeric",  "numeric", "text", "numeric", "date",  "date", "numeric", "numeric", "text",  "numeric", "numeric", "text", "date",  "date", "date", "text", "text", "text",   "text", "text", "text", "text", "text",  "text", "text", "text", "text", "text",  "text", "text", "text", "text", "text",  "text", "text", "text", "text", "text",  "text", "text", "text", "text", "text",  "text", "text", "text", "text", "text",  "text", "text", "text", "text", "text",  "text", "text", "text", "text", "text",  "numeric", "numeric", "numeric",  "numeric", "numeric", "numeric",  "numeric", "numeric", "numeric",  "numeric", "numeric", "numeric",  "numeric", "numeric", "numeric",  "numeric", "numeric", "numeric",  "numeric", "numeric", "numeric", "numeric", "numeric", "numeric", "numeric", "numeric", "numeric",   "numeric", "numeric", "numeric", 
 "numeric", "numeric", "numeric",  "numeric", "numeric", "numeric",  "numeric", "numeric", "numeric",  "numeric", "numeric", "numeric",  "numeric", "numeric", "numeric", "numeric", "numeric", "numeric",  "numeric", "numeric", "numeric",  "numeric", "numeric", "numeric",  "numeric", "numeric", "numeric",  "numeric", "numeric", "numeric",  "numeric", "numeric", "numeric",  "numeric", "numeric", "numeric",  "numeric", "numeric", "numeric",  "numeric", "numeric", "numeric",  "numeric", "numeric", "numeric",  "numeric", "numeric", "numeric",  "numeric", "numeric", "numeric",  "numeric", "numeric", "numeric",  "numeric", "numeric", "numeric",  "numeric", "numeric", "numeric",  "numeric", "numeric", "numeric",  "numeric", "numeric", "numeric",  "numeric", "numeric", "numeric",  "numeric", "numeric", "numeric",  "numeric", "numeric", "numeric",  "numeric", "numeric", "numeric",  "numeric", "numeric", "numeric",  "numeric", "numeric", "numeric",  "numeric", "numeric", "numeric",  "numeric", "numeric", "numeric",  "numeric", "numeric", "numeric",  "numeric", "numeric", "numeric",  "numeric", "numeric", "numeric", "numeric", "numeric", "numeric",  "numeric", "numeric", "numeric", "numeric", "numeric", "numeric", "numeric", "numeric", "numeric", "numeric", "numeric", "numeric", "numeric", "numeric", "numeric", "numeric", "numeric", "numeric", "numeric", "numeric", "numeric", "numeric", "numeric", "numeric", "numeric", "numeric", "text", "text", "text", "text", "text", "text", "text", "text", "text", "text", "text", "text", "text", "text", "text", "text", "text",  "text", "text", "text", "text", "text", "text", "text", "text", "text", "text", "text", "text", "text", "text", "text", "text", "text", "text", "text", "text", "text", "text", "text", "text", "text", "text"))

names(clinical_data)[names(clinical_data) == "Death (1=yes, 0=no)"] <- "Death"

names(clinical_data)[names(clinical_data) == "BRCA Mutation Detected (Y=Test Positive, N=Test Negative, N/A=Not tested)"] <- "BRCA Type"

names(clinical_data)[names(clinical_data) == "BRCA-mutation (Y=1, N=0, N/A = BLANK)"] <- "BRCA Binary"

names(clinical_data)[names(clinical_data) == "Recurrence...19"] <- "Recurence1"

names(clinical_data)[names(clinical_data) == "Recurrence...20"] <- "Recurence2"

names(clinical_data)[names(clinical_data) == "Recurrence...21"] <- "Recurence3"


## Note: There are 5 sample names in the distance data set that do not appear in the clinical data set. 

## Changing format for date of death to be able to grab the still alive as of. The clinical data set is being uploaded again so that the still alive as of can be reformatted into a date. It is then combined back into the original data set. The variable date of death now has solely dates as inputs and the column 'Death', which takes a binary input, distinguishes who is alive and dead for censoring purposes. 


clinical_data_part2 <- read_excel("~/Desktop/Research/MCR_Paper/data/Clinical_Attributes_and_more.xlsx", 
    col_types = c("numeric", "text", "numeric", 
        "text", "text", "numeric", "numeric", 
        "numeric", "text", "numeric", "text", 
        "text", "numeric", "numeric", "text", 
        "numeric", "numeric", "text", "text", 
        "text", "text", "text", "text", "text", 
        "text", "text", "text", "text", "text", 
        "text", "text", "text", "text", "text", 
        "text", "text", "text", "text", "text", 
        "text", "text", "text", "text", "text", 
        "text", "text", "text", "text", "text", 
        "text", "text", "text", "text", "text", 
        "text", "text", "text", "text", "text", 
        "text", "text", "text", "text", "text", 
        "numeric", "numeric", "numeric", 
        "numeric", "numeric", "numeric", 
        "numeric", "numeric", "numeric", 
        "numeric", "numeric", "numeric", 
        "numeric", "numeric", "numeric", 
        "numeric", "numeric", "numeric", 
        "numeric", "numeric", "numeric", 
        "numeric", "numeric", "numeric", 
        "numeric", "numeric", "numeric", 
        "numeric", "numeric", "numeric", 
        "numeric", "numeric", "numeric", 
        "numeric", "numeric", "numeric", 
        "numeric", "numeric", "numeric", 
        "numeric", "numeric", "numeric", 
        "numeric", "numeric", "numeric", 
        "numeric", "numeric", "numeric", 
        "numeric", "numeric", "numeric", 
        "numeric", "numeric", "numeric", 
        "numeric", "numeric", "numeric", 
        "numeric", "numeric", "numeric", 
        "numeric", "numeric", "numeric", 
        "numeric", "numeric", "numeric", 
        "numeric", "numeric", "numeric", 
        "numeric", "numeric", "numeric", 
        "numeric", "numeric", "numeric", 
        "numeric", "numeric", "numeric", 
        "numeric", "numeric", "numeric", 
        "numeric", "numeric", "numeric", 
        "numeric", "numeric", "numeric", 
        "numeric", "numeric", "numeric", 
        "numeric", "numeric", "numeric", 
        "numeric", "numeric", "numeric", 
        "numeric", "numeric", "numeric", 
        "numeric", "numeric", "numeric", 
        "numeric", "numeric", "numeric", 
        "numeric", "numeric", "numeric", 
        "numeric", "numeric", "numeric", 
        "numeric", "numeric", "numeric", 
        "numeric", "numeric", "numeric", 
        "numeric", "numeric", "numeric", 
        "numeric", "numeric", "numeric", 
        "numeric", "numeric", "numeric", 
        "numeric", "numeric", "numeric", 
        "numeric", "numeric", "numeric", 
        "numeric", "numeric", "numeric", 
        "numeric", "numeric", "numeric", 
        "numeric", "numeric", "numeric", 
        "numeric", "numeric", "numeric", 
        "numeric", "numeric", "numeric", 
        "numeric", "numeric", "numeric", 
        "numeric", "numeric", "numeric", 
        "numeric", "numeric", "numeric", 
        "numeric", "numeric", "text", "text", 
        "text", "text", "text", "text", "text", 
        "text", "text", "text", "text", "text", 
        "text", "text", "text", "text", "text", 
        "text", "text", "text", "text", "text", 
        "text", "text", "text", "text", "text", 
        "text", "text", "text", "text", "text", 
        "text", "text", "text", "text", "text", 
        "text", "text", "text", "text", "text", 
        "text"))

clinical_data_part2 = clinical_data_part2 %>% select(`Sample Name`, `Date of Death`)


#three different beginnings for alive as.... "Alive as", "Alive as of", "last visit" Below reformats all to "Alive as"

clinical_data_part2$`Date of Death` = gsub("last visit", "Alive as",clinical_data_part2$`Date of Death` )
#setting up format of variable to be able to use substr. Need to chance "last visit" to Alive as.

clinical_data_part2$`Date of Death` = gsub("Alive as of", "Alive as",clinical_data_part2$`Date of Death` )
# setting up format of variable to be able to use substr. Need to chance "Alive as of" to "Alive as".

clinical_data_part2$`Date of Death` = substr(clinical_data_part2$`Date of Death`, 10, 100)
#now cutting off the first 10 string characters 


#formatting characters into Dates

clinical_data_part2$`Date of Death` =  mdy(clinical_data_part2$`Date of Death`)


#combines Dates from original data set (deaths) and new dates (alive as of) into one variable 'Date of Death`. Seperate column identifies whether or not patients have actually died or not. 

clinical_data$`Date of Death` = coalesce(clinical_data$`Date of Death`, clinical_data_part2$`Date of Death`)



## Creating an overall survival time variable in clinical data set (date of death - date of diagnosis)

clinical_data$`Date of Death` = as.Date(clinical_data$`Date of Death`)
clinical_data$`Date of Diagnosis` = as.Date(clinical_data$`Date of Diagnosis`)


#Filtering clinical data down to the most important variables. The clinical data set has many variables, such as a calculation of total percentage of cells. We recalculated those as seen in the code below and so we take only relevant clinical attributes such as date of death. 
clinical_data = clinical_data[,1:29]
  

## changing date of death for sample A_Core[1,1,H]_[20830,38587].im3 to 8/7/2019 - in the data set, date is listed as 8/72019.

clinical_data = clinical_data %>% mutate(`Date of Death` = case_when(
  `Sample Name` == "A_Core[1,1,H]_[20830,38587].im3" ~ as.Date(mdy("8/7/2019")),
  TRUE ~ `Date of Death`
))


# Editing the debulking variable for typos and capitalization standardization 

clinical_data = clinical_data %>% mutate(Debulking= case_when(
  Debulking == "optimal" ~ "Optimal",
  Debulking == "Opitmal" ~ "Optimal",
   Debulking == "Optimal" ~ "Optimal",
   Debulking == "Suboptimal" ~ "Suboptimal",
  Debulking == "suboptimal" ~ "Suboptimal",
  Debulking == "Interval" ~ "Interval",
  TRUE ~ "NA",
))

clinical_data = clinical_data %>% replace_with_na(replace=list(Debulking=("NA")))
clinical_data$Debulking = factor(clinical_data$Debulking, ordered=FALSE)

#Variable for survival time 
clinical_data = clinical_data %>% group_by(`Sample Name`) %>% mutate(survival_time = `Date of Death` - `Date of Diagnosis`) %>% ungroup() 


# time to recurrence as numeric
clinical_data$`Time to recurrence` = as.numeric(clinical_data$`Time to recurrence`)

# recurrence binary 

clinical_data = clinical_data %>% group_by(`Sample Name`) %>% mutate(recurrence_binary = if_else(is.na(Recurence1), 0, 1)) %>% ungroup()

# time to event binary 

clinical_data = clinical_data %>% group_by(`Sample Name`) %>% mutate(time_to_event_binary = case_when(
  recurrence_binary == "1" ~ "1",
  Death == "1" ~ "1",
  TRUE ~ "0"
)) %>% ungroup()


clinical_data$time_to_event_binary = as.numeric(clinical_data$time_to_event_binary)

# Recurrence date formatting; looking at just the first date from the recurrence column. 

clinical_data$recurrence_date = ymd(clinical_data$Recurence1)

# time to recurrence
clinical_data$time_to_recurrence =  clinical_data$recurrence_date - clinical_data$`Date of Diagnosis`

# Need variable that is time to recurrence or survival time 

clinical_data = clinical_data %>% group_by(`Sample Name`) %>% mutate(time_to_event = if_else(is.na(time_to_recurrence), survival_time, time_to_recurrence)) %>% ungroup()


  
# Filtering down the ovarian data set to just mean expressions; originally included extra variables such as min, max, standard deviation; was trying to make later operations quicker by slimming down data set. 

ovarian_slim = ovarian_data %>% select(`Sample Name`, tag, Path, `Tissue Category`, `Cell ID`, `Cell X Position`, `Cell Y Position`, `Category Region ID`, `Distance from Tissue Category Edge (microns)`,`Nucleus Area (square microns)`, `Nucleus Area (percent)`, `Nucleus Compactness`, `Nucleus Minor Axis`, `Nucleus Major Axis`, `Nucleus Axis Ratio`, `Nucleus CK (Opal 780) Mean`, `Nucleus Ki67 (Opal 690) Mean`, `Nucleus CD8 (Opal 650) Mean`, `Nucleus IER3 (Opal 620) Mean`, `Nucleus pStat3 (Opal 570) Mean`, `Nucleus CD3 (Opal 540) Mean`, `Nucleus CD68 (Opal 520) Mean`, `Nucleus CD19 (Opal 480) Mean`, `Nucleus Dapi (DAPI) Mean`, `Nucleus Autofluorescence Mean`, `Cytoplasm Area (square microns)`, `Cytoplasm Area (percent)`, `Cytoplasm Compactness`, `Cytoplasm Minor Axis`, `Cytoplasm Major Axis`, `Cytoplasm Axis Ratio`,`Cytoplasm CK (Opal 780) Mean`, `Cytoplasm Ki67 (Opal 690) Mean`, `Cytoplasm CD8 (Opal 650) Mean`, `Cytoplasm IER3 (Opal 620) Mean`, `Cytoplasm pStat3 (Opal 570) Mean`, `Cytoplasm CD3 (Opal 540) Mean`, `Cytoplasm CD68 (Opal 520) Mean`, `Cytoplasm CD19 (Opal 480) Mean`, `Cytoplasm Dapi (DAPI) Mean`, `Cytoplasm Autofluorescence Mean`, `Membrane Area (square microns)`,`Membrane Area (percent)`, `Membrane Compactness`, `Membrane Minor Axis`, `Membrane Major Axis`, `Membrane Axis Ratio`, `Membrane CK (Opal 780) Mean`,`Membrane Ki67 (Opal 690) Mean`,  `Membrane CD8 (Opal 650) Mean`, `Membrane IER3 (Opal 620) Mean`,  `Membrane pStat3 (Opal 570) Mean`, `Membrane CD3 (Opal 540) Mean`,`Membrane CD68 (Opal 520) Mean`, `Membrane CD19 (Opal 480) Mean`, `Membrane Dapi (DAPI) Mean`, `Membrane Autofluorescence Mean`, `Entire Cell Area (square microns)` , `Entire Cell Area (percent)`, `Entire Cell Compactness`, `Entire Cell Minor Axis`, `Entire Cell Major Axis`, `Entire Cell Axis Ratio`, `Entire Cell CK (Opal 780) Mean`,`Entire Cell Ki67 (Opal 690) Mean`, `Entire Cell CD8 (Opal 650) Mean`, `Entire Cell IER3 (Opal 620) Mean`,`Entire Cell pStat3 (Opal 570) Mean`, `Entire Cell CD3 (Opal 540) Mean` , `Entire Cell CD68 (Opal 520) Mean` , `Entire Cell CD19 (Opal 480) Mean`, `Entire Cell Dapi (DAPI) Mean`, `Entire Cell Autofluorescence Mean`, `Slide ID`, `TMA Sector`, `TMA Row`,`TMA Column`, `TMA Field`, `Phenotype CD68`, `Phenotype CD19`, `Phenotype CD3`, `Phenotype CD8`, `Phenotype Ki67`, `Phenotype CD3 CD8`, `Phenotype CK`,  `Phenotype pStat3`)




image_with_clinical <- left_join(ovarian_slim, clinical_data, by = "Sample Name")



#creating event variable for Recur function
image_with_clinical = image_with_clinical %>% mutate(event = case_when(
  `Time to recurrence` >=0 ~2,
  TRUE ~1,
))



## Creating long data set and Phenotype variable 

ovarian_data_long = image_with_clinical %>% gather(key="pclassification", value="Phenotype", c(`Phenotype CD68`, `Phenotype Ki67`, `Phenotype CK`, `Phenotype CD19`, `Phenotype pStat3`, `Phenotype CD3`, `Phenotype CD8`, `Phenotype CD3 CD8`))


## Classifying Phenotypes into a cell type

ovarian_data_long = ovarian_data_long %>% mutate(`Cell Type` = case_when(
  Phenotype=="CD3+ CD8+" ~ "T Cell (CD8+)",
  Phenotype=="CD68+" ~ "Macrophage",
  Phenotype=="CK+" ~ "Tumor",
  Phenotype == "CD19+" ~ "B Cell",
  Phenotype=="CD3+ CD8-" ~ "T Cell (CD4+)",

  TRUE ~ "other"
))


# Filtering data to phenotypes of interest so cell totals / percents can be calculated quicker: 

ovarian_long_filtered = ovarian_data_long %>% filter(Phenotype %in% c("CD19+", "CD68+", "CK+", "pStat3+", "CD3+ CD8+", "CD3+ CD8-"))



# takes from ovarian_long_filtered; just the cells of interest
cell_totals = ovarian_long_filtered %>% group_by(`Sample Name`, `Phenotype`) %>% summarise(total_cells=n()) %>% arrange(Phenotype) %>% pivot_wider(names_from=Phenotype, values_from=total_cells)  %>% ungroup()
#^going back to long data set after filtering in order to table total cells and total cells in percents 

# takes from ovarian_data; need the total to come from all cells. 
totals_column = ovarian_data %>% group_by(`Sample Name`) %>% mutate(total=length(`Cell ID`)) %>% select(`Sample Name`, total) %>% unique() %>% arrange(`Sample Name`) %>% ungroup()
# creating variable for total cells for each sample


# Cell Counts totals and percent totals 

cell_totals = left_join(cell_totals, totals_column)
phenos <- c(unique(ovarian_long_filtered$Phenotype), "total")
cell_totals = cell_totals %>% arrange(`Sample Name`)



## Cell Percents by Phenotype
cell_totals = cell_totals %>% arrange(`Sample Name`) %>%  group_by(`Sample Name`) %>%  mutate(`CD19+ Percent`=round((`CD19+`/total)*100, 2),`CK+ Percent`=round((`CK+`/total)*100,2), `CD3+ CD8+ Percent`=round((`CD3+ CD8+`/total)*100,2),`CD3+ CD8- Percent`=round((`CD3+ CD8-`/total)*100,2), `CD68+ Percent`=round((`CD68+`/total)*100,2),  `pStat3+ Percent`= round((`pStat3+`/total)*100,2)) %>% ungroup()


# Cell totals Tumor

cell_totals_tumor = ovarian_long_filtered %>% filter(`Tissue Category`=="Tumor") %>% group_by(`Sample Name`, `Phenotype`) %>% summarise(total_cells=n()) %>% arrange(Phenotype) %>% pivot_wider(names_from=Phenotype, values_from=total_cells)  %>% ungroup()
#^going back to long data set after filtering in order to table total cells and total cells in percents 


totals_column_tumor = ovarian_data %>% filter(`Tissue Category`=="Tumor") %>%  group_by(`Sample Name`) %>% mutate(total=length(`Cell ID`)) %>% select(`Sample Name`, total) %>% unique() %>% arrange(`Sample Name`) %>% ungroup()
# creating variable for total cells for each sample


# Cell Counts totals and percent totals 

ovarian_long_filtered_tumor = ovarian_long_filtered %>% filter(`Tissue Category`=="Tumor")

cell_totals_tumor = left_join(cell_totals_tumor, totals_column_tumor)
phenos <- c(unique(ovarian_long_filtered_tumor$Phenotype), "total")
cell_totals_tumor = cell_totals_tumor %>% arrange(`Sample Name`)


# If there are zero cells of a specific cell type, the count function returns an NA. Changing NA values to zero 

cell_totals_tumor[is.na(cell_totals_tumor)] <- 0

## Cell Percents by Phenotype
cell_totals_tumor = cell_totals_tumor %>% arrange(`Sample Name`) %>%  group_by(`Sample Name`) %>%  mutate(`CD19+ Percent`=round((`CD19+`/total)*100, 2),`CK+ Percent`=round((`CK+`/total)*100,2), `CD3+ CD8+ Percent`=round((`CD3+ CD8+`/total)*100,2),`CD3+ CD8- Percent`=round((`CD3+ CD8-`/total)*100,2), `CD68+ Percent`=round((`CD68+`/total)*100,2),  `pStat3+ Percent`= round((`pStat3+`/total)*100,2)) %>% ungroup()


## setting up data set with one row for each sample so sample specific analysiis can be conducted (kaplan-meier and cox prorportional ) 

## Distance data frames 
## Macro_bcell

phenos <- c("CD68+", "CD19+")

# Calculating the nearest neighbor distance for each cell CD68+ and CD19+ cell. 

distance_macro_bcell <- ovarian_data_long %>% filter(Phenotype %in% c("CD68+", "CD19+")) %>% filter(`Tissue Category`=="Tumor") %>%
  group_by(`Slide ID`,`Sample Name`) %>%
  do(bind_cols(., find_nearest_distance(., phenos))) %>% ungroup()


# Counting the number of CD19+ Cells that have at least one CD68+ cell within 25 microns. 


count_within_macro_bcell = distance_macro_bcell %>% filter(`Tissue Category`=="Tumor")  %>% group_by(`Sample Name`) %>% 
  do(count_within(., from='CD19+', to='CD68+', radius=25)) %>% ungroup() 

#Selecting just the clinical variables neccesary, sample name, survival time, and death (for censoring)
clinical_data_count = image_with_clinical %>% select(`Sample Name`, survival_time, Death) %>% unique()


#Joining the cell totals in order to standardize the interaction variable across samples. 

count_within_macro_bcell = left_join(count_within_macro_bcell, clinical_data_count)
count_within_macro_bcell = left_join(count_within_macro_bcell, cell_totals_tumor)

count_within_macro_bcell = count_within_macro_bcell %>% group_by(`Sample Name`) %>% mutate(from_with_sd = (from_with/sum(`CD68+`,`CD19+`))*100) %>% ungroup()

# standardizing the from_with count by dividing each sample by the total number of b cells and macrophages for that sample and multiplying by 100 for a percent of b cells and macrophages within 25 microns of each other of total b cells and macrophages



count_within_macro_bcell = count_within_macro_bcell %>% mutate(distance_to_binary=case_when(
  from_with_sd > quantile(count_within_macro_bcell$from_with_sd, .5, na.rm=TRUE) ~ 1,
  TRUE ~ 0,
))

#reformatting names

names(count_within_macro_bcell)[names(count_within_macro_bcell) == "from_with"] <- "from_with_macro_bcell"
names(count_within_macro_bcell)[names(count_within_macro_bcell) == "from_with_sd"] <- "from_with_macro_bcell_standard"

## Removing the following sample from the cox_data set (which will include the survival curves because it does not have an exact date for date of death / last known alive. ? )

count_within_macro_bcell = count_within_macro_bcell %>% filter(`Sample Name` != "B_Core[1,1,B]_[7934,35665].im3")


# survival curve function  for Kaplan Meier
sf_distance = surv_fit(Surv(survival_time, Death) ~ distance_to_binary, data=count_within_macro_bcell)


# Selecting just sample size and from with counts from count_within_data frame

count1 =  count_within_macro_bcell %>% select(`Sample Name`, from_with_macro_bcell, from_with_macro_bcell_standard, distance_to_binary)


# Combining cell_totals_tumor with count_within_data


# Cox regression data - single row per sample - Cell totals in tumor regions, clinical data, distance data, 
cox_data = left_join(cell_totals_tumor, clinical_data)

cox_data = left_join(cox_data, count1)


#changing factor levels for debulking 
cox_data$Debulking = relevel(cox_data$Debulking, ref = "Optimal")

# changing Grade to factor and setting 3 as ref (most common)

cox_data$Grade = factor(cox_data$Grade)
cox_data$Grade = relevel(cox_data$Grade, ref = "3")


# Changing structure of PARPi variable to have 0 for no, 1 for yes. Setting as factor variable with reference 0
cox_data$PARPi = ifelse(cox_data$PARPi=="Y", 1, 0)
cox_data$PARPi= factor(cox_data$PARPi)
cox_data$PARPi = relevel(cox_data$PARPi, ref = "0")

# Setting Primary as factor variable with reference category = 1

cox_data$Primary = factor(cox_data$Primary)
cox_data$Primary = relevel(cox_data$Primary, ref = "1")


# Setting Treatment effect as a factor variable with reference category 0

cox_data$`Treatment Effect` = factor(cox_data$`Treatment Effect`)
cox_data$`Treatment Effect` = relevel(cox_data$`Treatment Effect`, ref = "0")


## Removing the following sample from the cox_data set (which will include the survival curves because it does not have an exact date for date of death / last known alive. ? )

cox_data = cox_data %>% filter(`Sample Name` != "B_Core[1,1,B]_[7934,35665].im3")


# Adding distance data frames for other cell combinations 

## from with 25 microns - from to CD3+ CD8+ to CD3+ CD8-

phenos <- c("CD3+ CD8+", "CD3+ CD8-")
# Calculating the nearest neighbor distance for each cell CD68+ and CD19+ cell. 

distance_cd4_tcell <- ovarian_data_long %>% filter(Phenotype %in% c("CD3+ CD8+", "CD3+ CD8-")) %>% filter(`Tissue Category`=="Tumor") %>%
  group_by(`Slide ID`,`Sample Name`) %>%
  do(bind_cols(., find_nearest_distance(., phenos))) %>% ungroup()


# Counting the number of CD19+ Cells that have at least one CD68+ cell within 25 microns. 


count_within_cd4_tcell = distance_cd4_tcell %>% filter(`Tissue Category`=="Tumor")  %>% group_by(`Sample Name`) %>% 
  do(count_within(., from='CD3+ CD8+', to='CD3+ CD8-', radius=25)) %>% ungroup() 

#Selecting just the clinical variables neccesary, sample name, survival time, and death (for censoring)
clinical_data_count = image_with_clinical %>% select(`Sample Name`, survival_time, Death) %>% unique()


#Joining the cell totals in order to standardize the interaction variable across samples. 

count_within_cd4_tcell = left_join(count_within_cd4_tcell, clinical_data_count)
count_within_cd4_tcell = left_join(count_within_cd4_tcell, cell_totals_tumor)

count_within_cd4_tcell = count_within_cd4_tcell %>% group_by(`Sample Name`) %>% mutate(from_with_sd = (from_with/sum(`CD3+ CD8+`, `CD3+ CD8-`))*100) %>% ungroup()

# standardizing the from_with count by dividing each sample by the total number of b cells and macrophages for that sample and multiplying by 100 for a percent of b cells and macrophages within 25 microns of each other of total b cells and macrophages

count_within_cd4_tcell = count_within_cd4_tcell %>% mutate(distance_to_binary=case_when(
  from_with_sd > quantile(count_within_cd4_tcell$from_with_sd, .5, na.rm=TRUE) ~ 1,
  TRUE ~ 0,
))

#70% at 21

names(count_within_cd4_tcell)[names(count_within_cd4_tcell) == "from_with"] <- "from_with_cd4_tcell"
names(count_within_cd4_tcell)[names(count_within_cd4_tcell) == "from_with_sd"] <- "from_with_cd4_tcell_standard"



## from with 25 microns - from CD3+ CD8+ to CD68+ 
phenos <- c("CD3+ CD8+", "CD68+")
# Calculating the nearest neighbor distance for each cell CD68+ and CD19+ cell. 

distance_tcell_macro <- ovarian_data_long %>% filter(Phenotype %in% c("CD3+ CD8+", "CD68+")) %>% filter(`Tissue Category`=="Tumor") %>%
  group_by(`Slide ID`,`Sample Name`) %>%
  do(bind_cols(., find_nearest_distance(., phenos))) %>% ungroup()


# Counting the number of CD19+ Cells that have at least one CD68+ cell within 25 microns. 


count_within_tcell_macro = distance_tcell_macro %>% filter(`Tissue Category`=="Tumor")  %>% group_by(`Sample Name`) %>% 
  do(count_within(., from='CD3+ CD8+', to='CD68+', radius=25)) %>% ungroup() 

#Selecting just the clinical variables neccesary, sample name, survival time, and death (for censoring)
clinical_data_count = image_with_clinical %>% select(`Sample Name`, survival_time, Death) %>% unique()


#Joining the cell totals in order to standardize the interaction variable across samples. 

count_within_tcell_macro = left_join(count_within_tcell_macro, clinical_data_count)
count_within_tcell_macro = left_join(count_within_tcell_macro, cell_totals_tumor)

count_within_tcell_macro = count_within_tcell_macro %>% group_by(`Sample Name`) %>% mutate(from_with_sd = (from_with/sum(`CD3+ CD8+`, `CD68+`))*100) %>% ungroup()

# standardizing the from_with count by dividing each sample by the total number of b cells and macrophages for that sample and multiplying by 100 for a percent of b cells and macrophages within 25 microns of each other of total b cells and macrophages

count_within_tcell_macro = count_within_tcell_macro %>% mutate(distance_to_binary=case_when(
  from_with_sd > quantile(count_within_tcell_macro$from_with_sd, .5, na.rm=TRUE) ~ 1,
  TRUE ~ 0,
))

#70% at 0.1170829 

names(count_within_tcell_macro)[names(count_within_tcell_macro) == "from_with"] <- "from_with_tcell_macro"
names(count_within_tcell_macro)[names(count_within_tcell_macro) == "from_with_sd"] <- "from_with_tcell_macro_standard"




## from with 25 microns - from CD3+ CD8- to CD68+ 
phenos <- c("CD3+ CD8-", "CD68+")
# Calculating the nearest neighbor distance for each cell CD68+ and CD19+ cell. 

distance_cd4_macro <- ovarian_data_long %>% filter(Phenotype %in% c("CD3+ CD8-", "CD68+")) %>% filter(`Tissue Category`=="Tumor") %>%
  group_by(`Slide ID`,`Sample Name`) %>%
  do(bind_cols(., find_nearest_distance(., phenos))) %>% ungroup()


# Counting the number of CD19+ Cells that have at least one CD68+ cell within 25 microns. 


count_within_cd4_macro = distance_cd4_macro %>% filter(`Tissue Category`=="Tumor")  %>% group_by(`Sample Name`) %>% 
  do(count_within(., from='CD3+ CD8-', to='CD68+', radius=25)) %>% ungroup() 

#Selecting just the clinical variables neccesary, sample name, survival time, and death (for censoring)
clinical_data_count = image_with_clinical %>% select(`Sample Name`, survival_time, Death) %>% unique()


#Joining the cell totals in order to standardize the interaction variable across samples. 

count_within_cd4_macro = left_join(count_within_cd4_macro, clinical_data_count)
count_within_cd4_macro = left_join(count_within_cd4_macro, cell_totals_tumor)

count_within_cd4_macro = count_within_cd4_macro %>% group_by(`Sample Name`) %>% mutate(from_with_sd = (from_with/sum(`CD3+ CD8-`, `CD68+`))*100) %>% ungroup()

# standardizing the from_with count by dividing each sample by the total number of b cells and macrophages for that sample and multiplying by 100 for a percent of b cells and macrophages within 25 microns of each other of total b cells and macrophages

count_within_cd4_macro = count_within_cd4_macro %>% mutate(distance_to_binary=case_when(
  from_with_sd > quantile(count_within_cd4_macro$from_with_sd, .5, na.rm=TRUE) ~ 1,
  TRUE ~ 0,
))

names(count_within_cd4_macro )[names(count_within_cd4_macro) == "from_with"] <- "from_with_cd4_macro"
names(count_within_cd4_macro )[names(count_within_cd4_macro) == "from_with_sd"] <- "from_with_cd4_macro_standard"

```

# Research Question:

* Do B Cells (CD19+) and Macrophages (CD68+) interact with each other in a meaningful way that leads to increased overall survival? 


# Table1 of variables

```{r}
# can change eval to TRUE if output is html

cox_data$status = factor(cox_data$Death, levels=c(0,1), labels = c("Alive", "Death"))

cox_data$`B Cell Macrophage Interaction Variable` = cox_data$from_with_macro_bcell_standard

my_table = table1(~  `B Cell Macrophage Interaction Variable` +`CD19+ Percent` + `CD68+ Percent`+`CD3+ CD8+ Percent`+ `CD3+ CD8- Percent` + `CK+ Percent` + `Age at Diagnosis`+ Grade  + Primary + `Treatment Effect` + Debulking + PARPi | status, data=cox_data %>% filter(`Sample Name` != "A_Core[1,1,H]_[20830,38587].im3"))

my_table 

# Note, do not have the survival time in here be cause the numbers may be misleading. Some of those (48) patients have censored data, which is taken into account in the cox and kaplan calculations but not in a simple summary.
```



# Cell Infiltrate - Kaplan Curves

* Note: at the 50th percentile, There were zero B cells interacting with either T Cells (CD3+ CD8+) or CD4 cells (CD3+ CD8-)



```{r}
## Survival curve for B Cell (CD19+) presence tumor region (count)


bcell_data = cox_data %>% select(survival_time, `CD19+ Percent`, `Sample Name`, Death, time_to_event_binary) %>% unique()

bcell_data = bcell_data  %>% mutate(bcell_percent_binary = case_when(
  `CD19+ Percent` >= quantile(`CD19+ Percent`, .5, na.rm = TRUE) ~ 1,
  TRUE~ 0
)) 


sf_bcell = surv_fit(Surv(survival_time, Death) ~ bcell_percent_binary, data=bcell_data)


macro_data = cox_data %>% select(survival_time, `CD68+ Percent`, `Sample Name`, Death) %>% unique()

macro_data = macro_data  %>% mutate(macro_percent_binary = case_when(
  `CD68+ Percent` >= quantile(`CD68+ Percent`, .5, na.rm=TRUE) ~ 1,
  TRUE~ 0
)) 


sf_macro = surv_fit(Surv(survival_time, Death) ~ macro_percent_binary, data=macro_data)

#Graph of Kaplan-Meier Curve

bcell_kaplan  = ggsurvplot(sf_bcell, 
   legend.title = "Cell Presence (CD19+)", 
   legend.labs = c("Low", "High"),
   #legend = c(7000, 0.8),
   font.legend = c(11, "bold", "black"),
   title = "A", 
   #subtitle = "",
   xlab = "Time (days)",
   font.title = c(14, "bold", "black"),
   #font.subtitle = c(12, "bold.italic", "black"),
   font.x = c(12, "bold.italic", "black"),
   font.y = c(16, "bold.italic", "black"),
   risk.table = FALSE, 
   ncensor.plot = FALSE,
   pval=TRUE,
   pval.size = 5,
   pval.coord = c(5400, 0.72),
   conf.int = TRUE
   ) 

bcell_kaplan$plot <- bcell_kaplan$plot+ 
              ggplot2::annotate("text", 
                                x = 6000, y = .8, # x and y coordinates of the text
                                label = "Hazard Ratio: 0.62", size = 5)



#coxph(Surv(survival_time, Death) ~ bcell_percent_binary, data =bcell_data ) %>% 
 # gtsummary::tbl_regression(exp = TRUE) 

```


```{r}
## Survival curve Macrophage (CD68+) presence tumor region (count)


#Graph of Kaplan-Meier Curve

macrophage_kaplan = ggsurvplot(sf_macro, 
   legend.title = "Cell Presence (CD68+)", 
   legend.labs = c("Low", "High"),
   #legend = c(.8, 0.8),
   font.legend = c(11, "bold", "black"),
   title = "B", 
  #subtitle = "",
   xlab = "Time (days)",
   ylab = NULL,
   font.title = c(14, "bold", "black"),
   #font.subtitle = c(12, "bold.italic", "black"),
   font.x = c(12, "bold.italic", "black"),
   font.y = c(12, "bold.italic", "black"),
   risk.table = FALSE, 
   ncensor.plot = FALSE,
   pval=TRUE,
   pval.size = 5,
   pval.coord = c(5400, 0.72),
   conf.int = TRUE
   ) 

macrophage_kaplan$plot <- macrophage_kaplan$plot+ 
              ggplot2::annotate("text", 
                                x = 6000, y = .8, # x and y coordinates of the text
                                label = "Hazard Ratio: 0.99 ", size = 5) 


#coxph(Surv(survival_time, Death) ~ macro_percent_binary, data =macro_data ) %>% 
#  gtsummary::tbl_regression(exp = TRUE) 

```


```{r}
## Survival curve for T Cell (CD8+) presence tumor region (count)


tcell_data = cox_data %>% select(survival_time, `CD3+ CD8+ Percent`, `Sample Name`, Death) %>% unique()

tcell_data = tcell_data  %>% mutate(tcell_count_binary = case_when(
  `CD3+ CD8+ Percent` >= quantile(`CD3+ CD8+ Percent`, .5, na.rm = TRUE) ~ 1,
  TRUE~ 0
)) 


sf_tcell = surv_fit(Surv(survival_time, Death) ~ tcell_count_binary, data=tcell_data)




#Graph of Kaplan-Meier Curve

tcell_kaplan = ggsurvplot(sf_tcell, 
           legend.title = "Cell Presence (CD8+)", 
           legend.labs = c("Low", "High"),
           font.legend = c(11, "bold", "black"),
           title = "C", 
           #subtitle = "",
           xlab = "Time (days)",
           font.title = c(14, "bold", "black"),
           #font.subtitle = c(12, "bold.italic", "black"),
           font.x = c(12, "bold.italic", "black"),
           font.y = c(16, "bold.italic", "black"),
           risk.table = FALSE,
           pval=TRUE,
           pval.size = 5,
           pval.coord = c(5400, 0.72),
           conf.int = TRUE) 


tcell_kaplan$plot <- tcell_kaplan$plot+ 
              ggplot2::annotate("text", 
                                x = 6000, y = .8, # x and y coordinates of the text
                                label = "Hazard Ratio:  0.78", size = 5)



#coxph(Surv(survival_time, Death) ~ tcell_count_binary, data = tcell_data ) %>% 
#  gtsummary::tbl_regression(exp = TRUE) 

surv_diff <- survdiff(Surv(survival_time, Death) ~ tcell_count_binary, data = tcell_data)
```



```{r}
## Survival curve for T Cell (CD4+) presence in whole sample (count)


cd4_data = cox_data %>% select(survival_time, `CD3+ CD8- Percent`, `Sample Name`, Death) %>% unique()

cd4_data = cd4_data  %>% mutate(cd4_count_binary = case_when(
  `CD3+ CD8- Percent` >= quantile(`CD3+ CD8- Percent`, .5, na.rm = TRUE) ~ 1,
  TRUE~ 0
)) 


sf_cd4 = surv_fit(Surv(survival_time, Death) ~ cd4_count_binary, data=cd4_data)


#Graph of Kaplan-Meier Curve
cd4_kaplan = ggsurvplot(sf_cd4, 
   legend.title = "Cell Presence (CD4+)", 
   legend.labs = c("Low", "High"),
   #legend = c(.8, 0.8),
    font.legend = c(11, "bold", "black"),
   title = "D", 
   #subtitle = "T",
   xlab = "Time (days)",
   ylab = NULL,
   font.title = c(14, "bold", "black"),
   #font.subtitle = c(12, "bold.italic", "black"),
   font.x = c(12, "bold.italic", "black"),
   font.y = c(16, "bold.italic", "black"),
   risk.table = FALSE, 
   ncensor.plot = FALSE,
   pval=TRUE,
   pval.size = 5,
   pval.coord = c(5400, 0.72),
   conf.int = TRUE
   ) 

cd4_kaplan$plot <- cd4_kaplan$plot+ 
              ggplot2::annotate("text", 
                                x = 6000, y = .8, # x and y coordinates of the text
                                label = "Hazard Ratio:  0.71", size = 5)


#coxph(Surv(survival_time, Death) ~ cd4_count_binary, data = cd4_data ) %>% 
#  gtsummary::tbl_regression(exp = TRUE) 


surv_diff <- survdiff(Surv(survival_time, Death) ~ cd4_count_binary, data = cd4_data)
```


```{r figure2, echo = FALSE, includE = TRUE, fig.align = "left", fig.width = 8, fig.height = 8}
# figure 2
x = list(bcell_kaplan, tcell_kaplan, macrophage_kaplan , cd4_kaplan)

graphs = arrange_ggsurvplots(x, 
  print = TRUE,
  title = NULL,
  ncol = 2,
  nrow = 2,
  surv.plot.height = NULL,
  risk.table.height = NULL,
  ncensor.plot.height = NULL,)

graphs
```
\textbf{Figure 2.} Kaplan-Meier curves for immune cell infiltration in tumor regions. A, Samples with a high percentage of B cell infiltration into tumor regions had higher overall survival probability compared to the low infiltration group (p=0.032). The Hazard ratio of 0.62 suggests that the samples with a high presence of B cells in tumor regions had 0.62 times the risk of hazard (death) compared to the low infiltration group (95% CI: 0.4 - 0.96).  B, Samples with a high percentage of macrophage infiltration into tumor regions did not differ significantly in survival probability from the low infiltration group (p=0.96). C, Samples with a high percentage of T cell (CD3+ CD8+) infiltration into tumor regions did not differ significantly in survival probability from the low infiltration group (p=0.26). D, Samples with a high percentage of CD4 T cell (CD3+ CD8-) infiltration into tumor regions did not differ significantly in survival probability from the low infiltration group (p=0.12). 



# Immune Cell Spatial Relationships - Binary classification - Hazard Ratio

*Note: the following analysis were also conducted but found to have not statistically significant results. 


## from with 25 microns - from CD19+ to CD68+ 

```{r}

sf_distance = surv_fit(Surv(survival_time, Death) ~ distance_to_binary, data=count_within_macro_bcell)

interaction_kaplan = ggsurvplot(sf_distance, main= "",
           legend.title = "Interaction (CD19+, CD68+)", 
           #legend = c(.8, 0.9),
           legend.labs = c("Low", "High"),
           font.legend = c(11, "bold", "black"),
           title = "A", 
          # subtitle = "",
           xlab = "Time (days)",
           font.title = c(14, "bold", "black"),
           #font.subtitle = c(12, "bold.italic", "black"),
           font.x = c(12, "bold.italic", "black"),
           font.y = c(16, "bold.italic", "black"),
           risk.table = FALSE,
           pval=TRUE,
           pval.size = 5,
           pval.coord = c(5400, 0.72),
           conf.int = TRUE
   ) 


interaction_kaplan$plot <- interaction_kaplan$plot+ 
              ggplot2::annotate("text", 
                                x = 6000, y = .8, # x and y coordinates of the text
                                label = "Hazard Ratio: 0.64", size = 5) 

sf_interaction = surv_fit(Surv(survival_time, Death) ~ distance_to_binary, data=cox_data)


surv_diff <- survdiff(Surv(survival_time, Death) ~ distance_to_binary, data = cox_data)
surv_diff


#binary distance to variable to get hazard ratio for kaplan
coxph(Surv(survival_time, Death) ~ distance_to_binary, data =  cox_data ) %>% 
  gtsummary::tbl_regression(exp = TRUE) 

```

## from with 25 microns - from CD3+ CD8+ to CD68+ 

```{r}


sf_distance = surv_fit(Surv(survival_time, Death) ~ distance_to_binary, data= count_within_tcell_macro)

tcell_macro_interaction = ggsurvplot(sf_distance, main= "Survival Curve for macrophage Total Cell Count in Tumor Regions" ,
           legend.title = "Interaction (CD8+, CD68+)", 
           legend.labs = c("Low", "High"),
           font.legend = c(11, "bold", "black"),
           title = "B", 
           #subtitle = "",
           xlab = "Time (days)",
           ylab = NULL,
           font.title = c(14, "bold", "black"),
           #font.subtitle = c(12, "bold.italic", "black"),
           font.x = c(12, "bold.italic", "black"),
           font.y = c(16, "bold.italic", "black"),
           risk.table = FALSE,
           pval=TRUE,
           pval.size = 5,
           pval.coord = c(5400, 0.72),
           conf.int = TRUE)

tcell_macro_interaction$plot <- tcell_macro_interaction$plot+ 
              ggplot2::annotate("text", 
                                x = 6000, y = .8, # x and y coordinates of the text
                                label = "Hazard Ratio: 0.85", size = 5)



coxph(Surv(survival_time, Death) ~ distance_to_binary, data = count_within_tcell_macro ) %>% 
  gtsummary::tbl_regression(exp = TRUE) 




```


## from with 25 microns - from CD3+ CD8- to CD68+ 

```{r}

sf_distance = surv_fit(Surv(survival_time, Death) ~ distance_to_binary, data=count_within_cd4_macro )

cd4_macro_interaction = ggsurvplot(sf_distance, main= "" ,
           legend.title = "Interaction (CD4+, CD68+)", 
           legend.labs = c("Low", "High"),
           font.legend = c(11, "bold", "black"),
           title = "C", 
           #subtitle = "",
           xlab = "Time (days)",
           font.title = c(14, "bold", "black"),
           #font.subtitle = c(12, "bold.italic", "black"),
           font.x = c(12, "bold.italic", "black"),
           font.y = c(16, "bold.italic", "black"),
           risk.table = FALSE,
           pval=TRUE,
           pval.size = 5,
           pval.coord = c(5400, 0.72),
           conf.int = TRUE) 

cd4_macro_interaction$plot <- cd4_macro_interaction$plot+ 
              ggplot2::annotate("text", 
                                x = 6000, y = .8, # x and y coordinates of the text
                                label = "Hazard Ratio: 0.85", size = 5)


coxph(Surv(survival_time, Death) ~ distance_to_binary, data = count_within_cd4_macro ) %>% 
  gtsummary::tbl_regression(exp = TRUE) 

```


## from with 25 microns - from to CD3+ CD8+ to CD3+ CD8-

```{r}


sf_distance = surv_fit(Surv(survival_time, Death) ~ distance_to_binary, data=count_within_cd4_tcell)

cd4_tcell_distance = ggsurvplot(sf_distance, main= "" ,
           legend.title = "Interaction (CD4+, CD8+)", 
           legend.labs = c("Low", "High"),
           font.legend = c(11, "bold", "black"),
           title = "D", 
           #subtitle = "",
           xlab = "Time (days)",
           ylab = NULL,
           font.title = c(14, "bold", "black"),
           #font.subtitle = c(12, "bold.italic", "black"),
           font.x = c(12, "bold.italic", "black"),
           font.y = c(16, "bold.italic", "black"),
           risk.table = FALSE,
           pval=TRUE,
           pval.size = 5,
           pval.coord = c(5400, 0.72),
           conf.int = TRUE) 

cd4_tcell_distance$plot <- cd4_tcell_distance$plot+ 
              ggplot2::annotate("text", 
                                x = 6000, y = .8, # x and y coordinates of the text
                                label = "Hazard Ratio: 0.88", size = 5)


coxph(Surv(survival_time, Death) ~ distance_to_binary, data = count_within_cd4_tcell ) %>% 
  gtsummary::tbl_regression(exp = TRUE) 

```


```{r, eval = FALSE}

# T Cells and B Cells 

phenos <- c("CD3+ CD8+", "CD19+")

# Calculating the nearest neighbor distance for each cell CD68+ and CD19+ cell. 

distance_macro_bcell <- ovarian_data_long %>% filter(Phenotype %in% c("CD3+ CD8+", "CD19+")) %>% filter(`Tissue Category`=="Tumor") %>%
  group_by(`Slide ID`,`Sample Name`) %>%
  do(bind_cols(., find_nearest_distance(., phenos))) %>% ungroup()


# Counting the number of CD19+ Cells that have at least one CD68+ cell within 25 microns. 


count_within_macro_bcell = distance_macro_bcell %>% filter(`Tissue Category`=="Tumor")  %>% group_by(`Sample Name`) %>% 
  do(count_within(., from='CD19+', to='CD3+ CD8+', radius=25)) %>% ungroup() 

#Selecting just the clinical variables neccesary, sample name, survival time, and death (for censoring)
clinical_data_count = image_with_clinical %>% select(`Sample Name`, survival_time, Death) %>% unique()


#Joining the cell totals in order to standardize the interaction variable across samples. 

count_within_macro_bcell = left_join(count_within_macro_bcell, clinical_data_count)
count_within_macro_bcell = left_join(count_within_macro_bcell, cell_totals_tumor)

count_within_macro_bcell = count_within_macro_bcell %>% group_by(`Sample Name`) %>% mutate(from_with_sd = (from_with/sum(`CD3+ CD8+`,`CD19+`))*100) %>% ungroup()

# standardizing the from_with count by dividing each sample by the total number of b cells and macrophages for that sample and multiplying by 100 for a percent of b cells and macrophages within 25 microns of each other of total b cells and macrophages



count_within_macro_bcell = count_within_macro_bcell %>% mutate(distance_to_binary=case_when(
  from_with_sd > quantile(count_within_macro_bcell$from_with_sd, .5, na.rm=TRUE) ~ 1,
  TRUE ~ 0,
))

names(count_within_macro_bcell)[names(count_within_macro_bcell) == "from_with"] <- "from_with_macro_bcell"
names(count_within_macro_bcell)[names(count_within_macro_bcell) == "from_with_sd"] <- "from_with_macro_bcell_standard"

## Removing the following sample from the cox_data set (which will include the survival curves because it does not have an exact date for date of death / last known alive. It does have a month though? )

count_within_macro_bcell = count_within_macro_bcell %>% filter(`Sample Name` != "B_Core[1,1,B]_[7934,35665].im3")


#count_within_macro_bcell$from_with_macro_bcell_standard[is.na(count_within_macro_bcell$from_with_macro_bcell_standard)] <- 0


crude_model =  coxph(Surv(survival_time, Death) ~ from_with_macro_bcell_standard, data=count_within_macro_bcell)
summary(crude_model)


# Note, 50% of samples do not have B cells and T cells within 25 microns of each other.
```


```{r, eval = FALSE}
# CD4 Cells and B Cells 


phenos <- c("CD3+ CD8-", "CD19+")

# Calculating the nearest neighbor distance for each cell CD68+ and CD19+ cell. 

distance_macro_bcell <- ovarian_data_long %>% filter(Phenotype %in% c("CD3+ CD8-", "CD19+")) %>% filter(`Tissue Category`=="Tumor") %>%
  group_by(`Slide ID`,`Sample Name`) %>%
  do(bind_cols(., find_nearest_distance(., phenos))) %>% ungroup()


# Counting the number of CD19+ Cells that have at least one CD68+ cell within 25 microns. 


count_within_macro_bcell = distance_macro_bcell %>% filter(`Tissue Category`=="Tumor")  %>% group_by(`Sample Name`) %>% 
  do(count_within(., from='CD19+', to='CD3+ CD8-', radius=25)) %>% ungroup() 

#Selecting just the clinical variables neccesary, sample name, survival time, and death (for censoring)
clinical_data_count = image_with_clinical %>% select(`Sample Name`, survival_time, Death) %>% unique()


#Joining the cell totals in order to standardize the interaction variable across samples. 

count_within_macro_bcell = left_join(count_within_macro_bcell, clinical_data_count)
count_within_macro_bcell = left_join(count_within_macro_bcell, cell_totals_tumor)

count_within_macro_bcell = count_within_macro_bcell %>% group_by(`Sample Name`) %>% mutate(from_with_sd = (from_with/sum(`CD3+ CD8-`,`CD19+`))*100) %>% ungroup()

# standardizing the from_with count by dividing each sample by the total number of b cells and macrophages for that sample and multiplying by 100 for a percent of b cells and macrophages within 25 microns of each other of total b cells and macrophages



count_within_macro_bcell = count_within_macro_bcell %>% mutate(distance_to_binary=case_when(
  from_with_sd > quantile(count_within_macro_bcell$from_with_sd, .5, na.rm=TRUE) ~ 1,
  TRUE ~ 0,
))

names(count_within_macro_bcell)[names(count_within_macro_bcell) == "from_with"] <- "from_with_macro_bcell"
names(count_within_macro_bcell)[names(count_within_macro_bcell) == "from_with_sd"] <- "from_with_macro_bcell_standard"

## Removing the following sample from the cox_data set (which will include the survival curves because it does not have an exact date for date of death / last known alive. It does have a month though? )

count_within_macro_bcell = count_within_macro_bcell %>% filter(`Sample Name` != "B_Core[1,1,B]_[7934,35665].im3")


#count_within_macro_bcell$from_with_macro_bcell_standard[is.na(count_within_macro_bcell$from_with_macro_bcell_standard)] <- 0


crude_model =  coxph(Surv(survival_time, Death) ~ from_with_macro_bcell_standard, data=count_within_macro_bcell)
summary(crude_model)

# Note, 50% of samples do not have B cells and CD 4 T cells within 25 microns of each other.

```


# distance relationships kaplan curves


```{r figure3, echo = FALSE, includE = TRUE, fig.align = "left", fig.width = 9, fig.height = 9}
# figure 3
x = list(interaction_kaplan, cd4_macro_interaction, tcell_macro_interaction,  cd4_tcell_distance)

graphs_int = arrange_ggsurvplots(x, 
  print = TRUE,
  title = NULL,
  ncol = 2,
  nrow = 2,
  surv.plot.height = NULL,
  risk.table.height = NULL,
  ncensor.plot.height = NULL,)

graphs_int
```
\textbf{Figure 3.} Kaplan-Meier curves for different combinations of cell distance interactions in tumor regions. A, Samples with a high percentage of B cells (CD19+) in close proximity to macrophages (CD68+) had higher overall survival probability compared to the low interaction group (p=0.046). The Hazard ratio of 0.64 suggests the samples with a high percentage of B cells in close proximity to macrophages had 0.64 times the risk of hazard (death) compared to the low group (95% CI: 0.41 - 0.99).  B, Samples with a high percentage of CD8+ T cells (CD3+ CD8+) in close proximity to macrophages (CD68+) did not differ significantly in survival probability from the low interaction group (p=0.47). C, Samples with a high percentage of CD4+ T cells (CD3+ CD8-) in close proximity to macrophages (CD68+) did not differ significantly in survival probability from the low interaction group (p=0.46). D, Samples with a high percentage of CD8+ T cells (CD3+ CD8+) in close proximity to CD4+ T cells (CD3+ CD8-) did not differ significantly in survival probability from the low interaction group (p=0.57). 


# B Cell Infiltrate

* Note: we highlight that B Cell infiltrate alone is not significant in the cox proportional hazard models though it's binary, high or low categories, are in the Kaplan-Meier curves. 

## B Cell Infiltrate - Crude Model

```{r}

crude_model =  coxph(Surv(survival_time, Death) ~ `CD19+ Percent`, data=cox_data)
summary(crude_model)

```

* The presence of B cells in tumor regions alone is not a significant predictor in the hazard risk for patients (p=0.27). The adjusted models, which include the clinical variables show this same result. 

##  B Cell Infiltrate - Adjusted model B Cell Presence

* including clinical data variables and B Cell Percentage
```{r}

full_model =  coxph(Surv(survival_time, Death) ~ `Age at Diagnosis`  + Primary + `Treatment Effect` + Debulking + PARPi +`CD19+ Percent`, data=cox_data)

summary(full_model)

```
* The presence of B cells in tumor regions alone is not a significant predictor in the hazard risk for patients (p=0.26).  

# Cox Regressions for Cell Distance Relationships

## Crude Model B Cell / Macrophage Relationship

```{r}

crude_model =  coxph(Surv(survival_time, Death) ~ from_with_macro_bcell_standard, data=cox_data)
summary(crude_model)


#coxph_df = broom::tidy(crude_model)

# Exponentiating estimates
#coxph_df$estimate = exp(coxph_df$estimate)
#coxph_df$conf.low = exp(coxph_df$conf.low)
#coxph_df$conf.high = exp(coxph_df$conf.high)

#coxph_df = coxph_df %>% select(term, estimate, conf.low, conf.high, p.value)

#coxph_df %>% knitr::kable(digits = 3) %>%
#  kable_classic(full_width = F, html_font = "Cambria", font_size = 22)
```
* a one percent increase in the interaction variable is associated with a 10% decrease (p=0.0427) in the hazard (risk) of death (95% CI: 0.0032 - 17.4 percent). 

## Adjusted Model clinical with B Cell / Macrophage  Spatial relationship - 25 micron distance threshhold


```{r}

full_model =  coxph(Surv(survival_time, Death) ~from_with_macro_bcell_standard + `Age at Diagnosis`  + Primary + `Treatment Effect` + Debulking + PARPi, data=cox_data)


coxph_df = round(as.tibble(summary(full_model)$conf.int), 3)

coxph_df = coxph_df %>% select(-`exp(-coef)`)

p_value =round(as.tibble(summary(full_model)$coefficients) %>% select(`Pr(>|z|)`), 3)
 
variables = (summary(full_model)$coefficients)[,0]


coxph_df = cbind(variables, coxph_df) %>% cbind(p_value)

coxph_df %>% knitr::kable() 
```
* a one percent increase in the interaction variable is associated with a 10.6% decrease (p= 0.0318) in the hazard (risk) of death (95% CI: 1 - 19.34 percent). 
* Additionally, a one year increase of age at diagnosis is associated with a 3% increase (p<0.05) in the hazard (risk) of death (95% CI: 0.5 - 5.5 percent). 


## Crude cox models for other cell spatial interaction combinations

```{R}
#cd4 t cell and CD8+ t cell 

crude_model =  coxph(Surv(survival_time, Death) ~ from_with_cd4_tcell_standard, data=count_within_cd4_tcell)
summary(crude_model)

# CD4 T cell and Macrophage (CD68+)
crude_model =  coxph(Surv(survival_time, Death) ~ from_with_cd4_macro_standard, data=count_within_cd4_macro)
summary(crude_model)

# T cell (CD8+) and Macrophage (CD68+)
crude_model =  coxph(Surv(survival_time, Death) ~ from_with_tcell_macro_standard, data=count_within_tcell_macro)
summary(crude_model)

```

# Primary Tumor analysis

## B Cell Infiltrate - Crude Model

```{r}

crude_model =  coxph(Surv(survival_time, Death) ~ `CD19+ Percent`, data=cox_data %>% filter(Primary == "1"))
summary(crude_model)

```

* The presence of B cells in tumor regions alone is not a significant predictor in the hazard risk for patients (p=0.27). The adjusted models, which include the clinical variables show this same result. 

##  B Cell Infiltrate - Adjusted model B Cell Presence

* including clinical data variables and B Cell Percentage
```{r}

full_model =  coxph(Surv(survival_time, Death) ~ `Age at Diagnosis`   + `Treatment Effect` + Debulking + PARPi +`CD19+ Percent`, data=cox_data  %>% filter(Primary == "1"))

summary(full_model)

```
* The presence of B cells in tumor regions alone is not a significant predictor in the hazard risk for patients (p=0.26).  


## Crude Model B Cell / Macrophage Relationship

```{r}

crude_model =  coxph(Surv(survival_time, Death) ~ from_with_macro_bcell_standard, data=cox_data  %>% filter(Primary == "1"))
summary(crude_model)


#coxph_df = broom::tidy(crude_model)

# Exponentiating estimates
#coxph_df$estimate = exp(coxph_df$estimate)
#coxph_df$conf.low = exp(coxph_df$conf.low)
#coxph_df$conf.high = exp(coxph_df$conf.high)

#coxph_df = coxph_df %>% select(term, estimate, conf.low, conf.high, p.value)

#coxph_df %>% knitr::kable(digits = 3) %>%
#  kable_classic(full_width = F, html_font = "Cambria", font_size = 22)
```
* a one percent increase in the interaction variable is associated with a 10% decrease (p=0.0427) in the hazard (risk) of death (95% CI: 0.0032 - 17.4 percent). 

## Adjusted Model clinical with B Cell / Macrophage  Spatial relationship - 25 micron distance threshhold


```{r}

full_model =  coxph(Surv(survival_time, Death) ~from_with_macro_bcell_standard + `Age at Diagnosis`  + `Treatment Effect` + Debulking + PARPi, data=cox_data  %>% filter(Primary == "1"))


coxph_df = round(as.tibble(summary(full_model)$conf.int), 3)

coxph_df = coxph_df %>% select(-`exp(-coef)`)

p_value =round(as.tibble(summary(full_model)$coefficients) %>% select(`Pr(>|z|)`), 3)
 
variables = (summary(full_model)$coefficients)[,0]


coxph_df = cbind(variables, coxph_df) %>% cbind(p_value)

coxph_df %>% knitr::kable() 
```

# Time to Event Variable 

* event is recurrence or death (whichever occurs first.)

```{r, eval = FALSE}
# recurrence binary 

clinical_data = clinical_data %>% group_by(`Sample Name`) %>% mutate(recurrence_binary = if_else(is.na(Recurence1), 0, 1)) %>% ungroup()

# time to event binary 

clinical_data = clinical_data %>% group_by(`Sample Name`) %>% mutate(time_to_event_binary = case_when(
  recurrence_binary == "1" ~ "1",
  Death == "1" ~ "1",
  TRUE ~ "0"
)) %>% ungroup()

# Recurrence date formatting; looking at just the first date from the recurrence column. 

clinical_data$recurrence_date = ymd(clinical_data$Recurence1)

# time to recurrence
clinical_data$time_to_recurrence =  clinical_data$recurrence_date - clinical_data$`Date of Diagnosis`

# Need variable that is time to recurrence or survival time 

clinical_data = clinical_data %>% group_by(`Sample Name`) %>% mutate(time_to_event = if_else(is.na(time_to_recurrence), survival_time, time_to_recurrence)) %>% ungroup()

```

## Kaplan meier curve for time to event - B Cell Infiltrate

```{r}
## Survival curve for B Cell (CD19+) presence tumor region (count)


bcell_data_rec = cox_data %>% select(time_to_event, `CD19+ Percent`, `Sample Name`, time_to_event_binary) %>% unique()

bcell_data_rec = bcell_data_rec  %>% mutate(bcell_percent_binary = case_when(
  `CD19+ Percent` >= quantile(`CD19+ Percent`, .5, na.rm = TRUE) ~ 1,
  TRUE~ 0
)) 


sf_bcell = surv_fit(Surv(time_to_event, time_to_event_binary) ~ bcell_percent_binary, data=bcell_data_rec)


#Graph of Kaplan-Meier Curve

bcell_kaplan  = ggsurvplot(sf_bcell, 
   legend.title = "Cell Presence (CD19+)", 
   legend.labs = c("Low", "High"),
   #legend = c(7000, 0.8),
   font.legend = c(11, "bold", "black"),
   title = "A", 
   #subtitle = "",
   xlab = "Time (days)",
   font.title = c(14, "bold", "black"),
   #font.subtitle = c(12, "bold.italic", "black"),
   font.x = c(12, "bold.italic", "black"),
   font.y = c(16, "bold.italic", "black"),
   risk.table = FALSE, 
   ncensor.plot = FALSE,
   pval=TRUE,
   pval.size = 5,
   conf.int = TRUE
   ) 

bcell_kaplan$plot <- bcell_kaplan$plot+ 
              ggplot2::annotate("text", 
                                x = 6000, y = .8, # x and y coordinates of the text
                                label = "Hazard Ratio: 0.62", size = 5)

bcell_kaplan

#sf_bcell

```


* Median time to event (recurrence or death) for high b cell percent samples is 686 (95 CI: 615 - 884) vs low percentage median of 638 (95 CI: 571 - 864)
* In high b cell groups, 6 with no event and 62 with event and in low group, 7 with no event and 53 with event. 
 
 
## Kaplan meier curve for time to event - B Cell Macro relation

```{r}
sf_distance = surv_fit(Surv(time_to_event, as.numeric(time_to_event_binary)) ~ distance_to_binary, data=cox_data)

interaction_kaplan = ggsurvplot(sf_distance, main= "",
           legend.title = "Interaction (CD19+, CD68+)", 
           #legend = c(.8, 0.9),
           legend.labs = c("Low", "High"),
           font.legend = c(11, "bold", "black"),
           title = "A", 
          # subtitle = "",
           xlab = "Time (days)",
           font.title = c(14, "bold", "black"),
           #font.subtitle = c(12, "bold.italic", "black"),
           font.x = c(12, "bold.italic", "black"),
           font.y = c(16, "bold.italic", "black"),
           risk.table = FALSE,
           pval=TRUE,
           pval.size = 5,
           #pval.coord = c(5400, 0.72),
           conf.int = TRUE
   ) 


interaction_kaplan$plot <- interaction_kaplan$plot+ 
              ggplot2::annotate("text", 
                                x = 6000, y = .8, # x and y coordinates of the text
                                label = "Hazard Ratio: 0.86", size = 5) 

sf_interaction = surv_fit(Surv(time_to_event, time_to_event_binary) ~ distance_to_binary, data=cox_data)


surv_diff <- survdiff(Surv(time_to_event, time_to_event_binary) ~ distance_to_binary, data = cox_data)
surv_diff


#binary distance to variable to get hazard ratio for kaplan
coxph(Surv(time_to_event, time_to_event_binary) ~ distance_to_binary, data =  cox_data ) %>% 
  gtsummary::tbl_regression(exp = TRUE) 

interaction_kaplan
```

* Median time to event for high b cell macro interaction is 790 (95 CI: 651 - 1066) vs median for low group 610 ( 95 CI: 510 - 770)
* In the high interaction group, there are 7 people with no event and 53 with event. In the low interaction group, there are 6 with no event and 61 with event. 

## Cox Proportional - B cell infiltrate - Time To event (recurrence or death)

```{r}

full_model =  coxph(Surv(time_to_event, time_to_event_binary) ~ `CD19+ Percent` + `Age at Diagnosis`  + Primary + `Treatment Effect` + Debulking + PARPi, data=cox_data)


coxph_df = round(as.tibble(summary(full_model)$conf.int), 3)

coxph_df = coxph_df %>% select(-`exp(-coef)`)

p_value =round(as.tibble(summary(full_model)$coefficients) %>% select(`Pr(>|z|)`), 3)
 
variables = (summary(full_model)$coefficients)[,0]


coxph_df = cbind(variables, coxph_df) %>% cbind(p_value)

coxph_df %>% knitr::kable() 

```



## Crude Cox Proportional - B Cell Macro relation - Time To event (recurrence or death)

```{r}
crude_model =  coxph(Surv(time_to_event, time_to_event_binary) ~ from_with_macro_bcell_standard, data=cox_data)
summary(crude_model)



#coxph_df = broom::tidy(crude_model)

# Exponentiating estimates
#coxph_df$estimate = exp(coxph_df$estimate)
#coxph_df$conf.low = exp(coxph_df$conf.low)
#coxph_df$conf.high = exp(coxph_df$conf.high)

#coxph_df = coxph_df %>% select(term, estimate, conf.low, conf.high, p.value)

#coxph_df %>% knitr::kable(digits = 3) %>%
#  kable_classic(full_width = F, html_font = "Cambria", font_size = 22)
```


## Adjusted Model clinical with B Cell / Macrophage Interaction - Time To event (recurrence or death)


```{r}

full_model =  coxph(Surv(time_to_event, time_to_event_binary) ~from_with_macro_bcell_standard + `Age at Diagnosis`  + Primary + `Treatment Effect` + Debulking + PARPi, data=cox_data)


coxph_df = round(as.tibble(summary(full_model)$conf.int), 3)

coxph_df = coxph_df %>% select(-`exp(-coef)`)

p_value =round(as.tibble(summary(full_model)$coefficients) %>% select(`Pr(>|z|)`), 3)
 
variables = (summary(full_model)$coefficients)[,0]


coxph_df = cbind(variables, coxph_df) %>% cbind(p_value)

coxph_df %>% knitr::kable() 

```

# Distance Variations for B Cell Macro

## Adjusted Model clinical with B Cell / Macrophage  Spatial relationship - 20 micron distance threshhold

```{r, eval = FALSE}
count_within_macro_bcell = distance_macro_bcell %>% filter(`Tissue Category`=="Tumor")  %>% group_by(`Sample Name`) %>% 
  do(count_within(., from='CD19+', to='CD68+', radius=20)) %>% ungroup() 

#Selecting just the clinical variables neccesary, sample name, survival time, and death (for censoring)
clinical_data_count = image_with_clinical %>% select(`Sample Name`, survival_time, Death) %>% unique()


#Joining the cell totals in order to standardize the interaction variable across samples. 

count_within_macro_bcell = left_join(count_within_macro_bcell, clinical_data_count)
count_within_macro_bcell = left_join(count_within_macro_bcell, cell_totals_tumor)

count_within_macro_bcell = count_within_macro_bcell %>% group_by(`Sample Name`) %>% mutate(from_with_sd = (from_with/sum(`CD68+`,`CD19+`))*100) %>% ungroup()

# standardizing the from_with count by dividing each sample by the total number of b cells and macrophages for that sample and multiplying by 100 for a percent of b cells and macrophages within 25 microns of each other of total b cells and macrophages



count_within_macro_bcell = count_within_macro_bcell %>% mutate(distance_to_binary=case_when(
  from_with_sd > quantile(count_within_macro_bcell$from_with_sd, .5, na.rm=TRUE) ~ 1,
  TRUE ~ 0,
))

#reformatting names

names(count_within_macro_bcell)[names(count_within_macro_bcell) == "from_with"] <- "from_with_macro_bcell"
names(count_within_macro_bcell)[names(count_within_macro_bcell) == "from_with_sd"] <- "from_with_macro_bcell_standard"

## Removing the following sample from the cox_data set (which will include the survival curves because it does not have an exact date for date of death / last known alive. ? )

count_within_macro_bcell = count_within_macro_bcell %>% filter(`Sample Name` != "B_Core[1,1,B]_[7934,35665].im3")


# survival curve function  for Kaplan Meier
sf_distance = surv_fit(Surv(survival_time, Death) ~ distance_to_binary, data=count_within_macro_bcell)


# Selecting just sample size and from with counts from count_within_data frame

count1 =  count_within_macro_bcell %>% select(`Sample Name`, from_with_macro_bcell, from_with_macro_bcell_standard, distance_to_binary)


# Combining cell_totals_tumor with count_within_data


# Cox regression data - single row per sample - Cell totals in tumor regions, clinical data, distance data, 
cox_data = left_join(cell_totals_tumor, clinical_data)

cox_data = left_join(cox_data, count1)


#changing factor levels for debulking 
cox_data$Debulking = relevel(cox_data$Debulking, ref = "Optimal")

# changing Grade to factor and setting 3 as ref (most common)

cox_data$Grade = factor(cox_data$Grade)
cox_data$Grade = relevel(cox_data$Grade, ref = "3")


# Changing structure of PARPi variable to have 0 for no, 1 for yes. Setting as factor variable with reference 0
cox_data$PARPi = ifelse(cox_data$PARPi=="Y", 1, 0)
cox_data$PARPi= factor(cox_data$PARPi)
cox_data$PARPi = relevel(cox_data$PARPi, ref = "0")

# Setting Primary as factor variable with reference category = 1

cox_data$Primary = factor(cox_data$Primary)
cox_data$Primary = relevel(cox_data$Primary, ref = "1")


# Setting Treatment effect as a factor variable with reference category 0

cox_data$`Treatment Effect` = factor(cox_data$`Treatment Effect`)
cox_data$`Treatment Effect` = relevel(cox_data$`Treatment Effect`, ref = "0")


full_model =  coxph(Surv(survival_time, Death) ~from_with_macro_bcell_standard + `Age at Diagnosis`  + Primary + `Treatment Effect` + Debulking + PARPi, data=cox_data)


coxph_df = round(as.tibble(summary(full_model)$conf.int), 3)

coxph_df = coxph_df %>% select(-`exp(-coef)`)

p_value =round(as.tibble(summary(full_model)$coefficients) %>% select(`Pr(>|z|)`), 3)
 
variables = (summary(full_model)$coefficients)[,0]


coxph_df = cbind(variables, coxph_df) %>% cbind( p_value)

coxph_df %>% knitr::kable() 
```

## Adjusted Model clinical with B Cell / Macrophage  Spatial relationship - 30 micron distance threshhold

```{r, eval = FALSE}
count_within_macro_bcell = distance_macro_bcell %>% filter(`Tissue Category`=="Tumor")  %>% group_by(`Sample Name`) %>% 
  do(count_within(., from='CD19+', to='CD68+', radius=30)) %>% ungroup() 

#Selecting just the clinical variables neccesary, sample name, survival time, and death (for censoring)
clinical_data_count = image_with_clinical %>% select(`Sample Name`, survival_time, Death) %>% unique()


#Joining the cell totals in order to standardize the interaction variable across samples. 

count_within_macro_bcell = left_join(count_within_macro_bcell, clinical_data_count)
count_within_macro_bcell = left_join(count_within_macro_bcell, cell_totals_tumor)

count_within_macro_bcell = count_within_macro_bcell %>% group_by(`Sample Name`) %>% mutate(from_with_sd = (from_with/sum(`CD68+`,`CD19+`))*100) %>% ungroup()

# standardizing the from_with count by dividing each sample by the total number of b cells and macrophages for that sample and multiplying by 100 for a percent of b cells and macrophages within 25 microns of each other of total b cells and macrophages



count_within_macro_bcell = count_within_macro_bcell %>% mutate(distance_to_binary=case_when(
  from_with_sd > quantile(count_within_macro_bcell$from_with_sd, .5, na.rm=TRUE) ~ 1,
  TRUE ~ 0,
))

#reformatting names

names(count_within_macro_bcell)[names(count_within_macro_bcell) == "from_with"] <- "from_with_macro_bcell"
names(count_within_macro_bcell)[names(count_within_macro_bcell) == "from_with_sd"] <- "from_with_macro_bcell_standard"

## Removing the following sample from the cox_data set (which will include the survival curves because it does not have an exact date for date of death / last known alive. ? )

count_within_macro_bcell = count_within_macro_bcell %>% filter(`Sample Name` != "B_Core[1,1,B]_[7934,35665].im3")


# survival curve function  for Kaplan Meier
sf_distance = surv_fit(Surv(survival_time, Death) ~ distance_to_binary, data=count_within_macro_bcell)


# Selecting just sample size and from with counts from count_within_data frame

count1 =  count_within_macro_bcell %>% select(`Sample Name`, from_with_macro_bcell, from_with_macro_bcell_standard, distance_to_binary)


# Combining cell_totals_tumor with count_within_data


# Cox regression data - single row per sample - Cell totals in tumor regions, clinical data, distance data, 
cox_data = left_join(cell_totals_tumor, clinical_data)

cox_data = left_join(cox_data, count1)


#changing factor levels for debulking 
cox_data$Debulking = relevel(cox_data$Debulking, ref = "Optimal")

# changing Grade to factor and setting 3 as ref (most common)

cox_data$Grade = factor(cox_data$Grade)
cox_data$Grade = relevel(cox_data$Grade, ref = "3")


# Changing structure of PARPi variable to have 0 for no, 1 for yes. Setting as factor variable with reference 0
cox_data$PARPi = ifelse(cox_data$PARPi=="Y", 1, 0)
cox_data$PARPi= factor(cox_data$PARPi)
cox_data$PARPi = relevel(cox_data$PARPi, ref = "0")

# Setting Primary as factor variable with reference category = 1

cox_data$Primary = factor(cox_data$Primary)
cox_data$Primary = relevel(cox_data$Primary, ref = "1")


# Setting Treatment effect as a factor variable with reference category 0

cox_data$`Treatment Effect` = factor(cox_data$`Treatment Effect`)
cox_data$`Treatment Effect` = relevel(cox_data$`Treatment Effect`, ref = "0")


full_model =  coxph(Surv(survival_time, Death) ~from_with_macro_bcell_standard + `Age at Diagnosis`  + Primary + `Treatment Effect` + Debulking + PARPi, data=cox_data)


coxph_df = round(as.tibble(summary(full_model)$conf.int), 3)

coxph_df = coxph_df %>% select(-`exp(-coef)`)

p_value =round(as.tibble(summary(full_model)$coefficients) %>% select(`Pr(>|z|)`), 3)
 
variables = (summary(full_model)$coefficients)[,0]


coxph_df = cbind(variables, coxph_df) %>% cbind(p_value)

coxph_df %>% knitr::kable() 

full_model %>% 
  gtsummary::tbl_regression(exp = TRUE) 
```

